Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices

### 2016-11-11 Presentation/gpm_november2016_vianello.tex
stareting to do TCV shot plan
ALmost done

\section{Topic 21 experiments }
\begin{frame}{$n_{\text{proposed shots}} \gg n_{\text{allocated shots}}$}
	\begin{itemize}
		\item 15 proposals submitted to Topic 21
		\item Proposals include experiments on all three machines 
		\item There are overlaps between several of the proposals 
		\item Preliminary shot allocation. AUG: 14. MAST: 13. TCV: 23
		\item However, total number of proposed shots:  \textbf{449}
		\item Several of the proposed experiments can be combined. \underline{But we must prioritize}
		\item Reaching all goals is not possible with the current number of allocated shots.
	\end{itemize}
\end{frame}

@@

\begin{frame}{H-mode experiments}
\begin{itemize}
	\item ITER and DEMO will operate in H-mode
	\item We must know what parameters control shoulder formation 
	\item Shoulder formation parameter regime is unclear on all machines
	\item Main priorities: 
	\begin{enumerate}
		\item Investigate if clear shoulder formation exists and what plasma parameters required? 
		\item Investigate the SOL (filamentary) transport properties. Main diagnostic is reciprocating probes $\rightarrow$ limits heating power
		\item Experiments must gradually increase power and density. 
	\end{enumerate}
	\item Fueling in H-mode is problematic due to transport barrier? 
\end{itemize}

@@

\begin{frame}{Proposed shot plan - AUG}
\vspace{-1cm}
Allocated shots $\sim$ 14 + contingency 
\begin{itemize}
	\item L-Mode (6 shots)
	\begin{enumerate}
		\item Reference shot \# 30276
		\item Perform $I_p$ scan (three values) with fixed $B_T$
		\item Perform $I_p$ scan fixing  $q_{95}$	 ($B_T$)	
		\item $B_T= 2.0$ required by proposal 6 (Aguiam). Should be possible for some shots? 		
		\item These shots combines experiments proposed by: Carralero, Militello, 	Vianello

@@

\begin{frame}{Proposed shot plan - TCV}

\begin{frame}{With aloocated shot we cannot do interesting stuff }
\begin{itemize}
	\item Ion temp measurements
	\item Topology investigations
	\item Strikepoint sweeping and cryo pump
	\item Parameters scans in H-mode
	\item Strike-point sweep

@@

\begin{frame}{piggybag on Quescient H-mode shots}
\end{frame}

\begin{frame}{Discussion agenda}

\begin{frame}{Future}
	meetings

	wiki

	Decisions made here uploaded to wiki

	Form experiment planning groups for each machine

\end{frame}
  % \only<1>{
% \begin{itemize}
% \item Role of turbulence transport in the SOL saturation is a well
%   know
%   feature \parencite{LaBombard:2001ks,Rudakov:2005ic,Garcia:2007hh,Carralero:2014gs}. \textcolor{red}{Increasing
%   density, even without reaching detachment SOL profile tend to flatten}
% \end{itemize}}
% \only<2-3>{
%   \begin{columns}
%     \begin{column}{0.5\textwidth}
%       \begin{itemize}
%       \item Present understanding suggests that a transition of filament
%         propagation regime is dominated by effective
%         collisionality $\Lambda$ \parencite{Myra:2006p2754}
%         \begin{equation*}
%           \Lambda = \frac{L_{\parallel}/c_s}{1/\nu_{ei}}\frac{\Omega_i}{\Omega_e}
%         \end{equation*}
%         \item<3> \textcolor{red}{At constant blob size, increasing
%             collisionality provide a change in the filaments velocity
%             scaling properties}
%       \end{itemize}
%     \end{column}
%     \begin{column}{0.5\textwidth}
% %      \includegraphics<2>[width=\textwidth]{../pdfbox/Presentation/FigMyra}
%         \begin{tikzonimage}[width=\textwidth]{../pdfbox/Presentation/FigMyra}
%           \only<3>{
%             \draw [->, ultra thick, red] (0.7,0.3) -- (0.7,0.6);}
%         \end{tikzonimage}
%     \end{column}
%   \end{columns}
% }
% \only<4-6>{
%   \begin{columns}
%     \begin{column}{0.5\textwidth}
%       \begin{itemize}
%       \item AUG and JET \parencite{Carralero:2015gu} suggest that $\Lambda_{div}$ dominates this
%         process and a transition from
%         \textcolor{ta3chameleon}{sheath-limited}
%         \onslide<5-6>{to \textcolor{blue}{inertial regime}} 
%         \item<6> \textcolor{red}{Tested by changing n$_e$
%             and $T_e$ through fueling/seeding/heating}
%       \end{itemize}
%     \end{column}
%     \begin{column}{0.5\textwidth}
%       \begin{tikzonimage}[width=\textwidth]{../pdfbox/Presentation/KoMFig2.png}
%         \only<4-6>{
%           \draw [thick, ta3chameleon, thick] (0.45,0.25) ellipse (0.23 and 0.1);
%       }
%         \only<5-6>{
%           \draw [thick, blue, thick, rotate=-4] (0.8,0.55) ellipse (0.1 and 0.33);
%       }
%         \only<6>{
%           \draw [thick, red, thick, dashed] (0.35,0.75) circle (0.25);
%       }
%     \end{tikzonimage}
%   \end{column}
%   \end{columns}
% }
% \only<7->{
%   \begin{columns}
%     \begin{column}{0.5\textwidth}
%       \begin{itemize}
%       \item MAST \parencite{Militello:2016hk} and old TCV
%         \parencite{Garcia:2007p2615} data 
%         suggested and I$_P$ dependence. 
%           \textcolor{red}{At higher current and
%         same density SOL shoulder disappear} 
%       \item<8> \textcolor{ta3chameleon}{Being shoulder formation
%           induced by a change of $\Gamma_{\perp}$ \textit{vs}
%           $\Gamma_{\parallel}$ balance we will try to test dependence
%           on L$_{\parallel}$}
%     \end{itemize}
%     \end{column}
%     \begin{column}{0.5\textwidth}
%       \includegraphics[width=\textwidth]{../pdfbox/Presentation/FigMilitello.pdf}
%     \end{column}
%   \end{columns}
% }
% \centering{\includegraphics<1>[width=1.1\textwidth]{../pdfbox/Presentation/Fig1Presentation}}
% \end{frame}

>>>>

\section{Topic 21 experiments }
\begin{frame}{$n_{\text{proposed shots}} \gg n_{\text{allocated shots}}$}
	\begin{itemize}
		\item 15 proposals submitted to Topic 21
		\item Proposals include experiments on all three machines 
		\item There are overlaps between several of the proposals 
		\item Preliminary shot allocation. AUG: 14. MAST: 13. TCV: 23 !!!!!!!1SHOULD WE ADD PRELIMINARY DATES FOR THE EXPERIMENTS??
		\item However, total number of proposed shots:  \textbf{449}
		\item Several of the proposed experiments can be combined. \underline{But we must prioritize}
		\item Reaching all goals is not possible with the current number of allocated shots.
	\end{itemize}
\end{frame}

@@

\begin{frame}{H-mode experiments}
\begin{itemize}
	\item ITER and DEMO will operate in H-mode
	\item We must know what parameters control shoulder formation 
	\item Shoulder formation parameter regime is unclear on all machines
	\item Main priorities: 
	\begin{enumerate}
		\item Investigate if clear shoulder formation exists and what plasma parameters required? 
		\item Investigate the SOL (filamentary) transport properties. Main diagnostic is reciprocating probes $\rightarrow$ limits heating power
		\item Experiments must gradually increase power and density. 
	\end{enumerate}
	\item Fueling in H-mode is problematic due to transport barrier? NBI fueling?
	\item H-mode density limit\parencite{Bernert:2015ppcf} must be avoided
\end{itemize}

@@

\begin{frame}{Proposed shot plan - AUG}
\vspace{-1cm}
Allocated shots $\sim$ 14 + contingency 
\begin{itemize}
	\item L-Mode (6 shots)
	\begin{enumerate}
		\item Reference shot \# 30276
		\item Perform $I_p$ scan (three values) with fixed $B_T$
		\item Perform $I_p$ scan fixing  $q_{95}$	 ($B_T$)	
		\item $B_T= 2.0$ required by proposal 6 (Aguiam). Should be possible for some shots? 		
		\item should we add OM puff to validate neutral measurements?
		\item These shots combines experiments proposed by: Carralero, Militello, 	Vianello

@@

\begin{frame}{Proposed shot plan - TCV}
	\begin{itemize}
		\item L-mode (11 shots)
		\begin{enumerate}
			\item Reference shot \# 53514
			\item Same $I_p$ and $q_{95}$ scans as on AUG
			\item Two shots with reversed $\bm{B} \times \nabla B$
			\item Move plasma vertically. Disentangle $q_{95}$ and $L_{\|}$			
		\end{enumerate}
		\item H-mode (12 shots)
		\begin{enumerate}
			\item Reference shot \# 53352
			\item Since H-mode shoulder is new territory on TCV first shots will be scenario development
			\item As on AUG. Incremental increases of power and density. Close monitoring the midplane probe. 
		\end{enumerate}
	\end{itemize}
\end{frame}

\begin{frame}{Preliminary shot plan  - MAST-U}
	\begin{itemize}
		\item 
	\end{itemize}
\end{frame}

\begin{frame}{There are urgent experiment which cannot be addressed}
\begin{itemize}
	\item Ion temp measurements
	\item Topology investigations
	\item Strikepoint sweeping and cryo pump
	\item Parameters scans in H-mode
	\item Strike-point sweep

@@

\begin{frame}{Future and Miscellaneous}
	\begin{itemize}
		\item piggybag on Quescient H-mode shots
		\item Shortly after this meeting we will organize a follow-up meeting to reconcile ideas from this discussion (date not fixed yet)
		\item All information will be gathered on the wiki

\begin{frame}{Discussion agenda}
	\begin{enumerate}
		\item Priorities. Do we agree? 
		\item Common measurement techniques. E.g. $I_{sat}$ instead if $\phi_f$ for filament velocities?
		\item Publications
 	\end{enumerate}
\end{frame}

  % \only<1>{
% \begin{itemize}
% \item Role of turbulence transport in the SOL saturation is a well
%   know
%   feature \parencite{LaBombard:2001ks,Rudakov:2005ic,Garcia:2007hh,Carralero:2014gs}. \textcolor{red}{Increasing
%   density, even without reaching detachment SOL profile tend to flatten}
% \end{itemize}}
% \only<2-3>{
%   \begin{columns}
%     \begin{column}{0.5\textwidth}
%       \begin{itemize}
%       \item Present understanding suggests that a transition of filament
%         propagation regime is dominated by effective
%         collisionality $\Lambda$ \parencite{Myra:2006p2754}
%         \begin{equation*}
%           \Lambda = \frac{L_{\parallel}/c_s}{1/\nu_{ei}}\frac{\Omega_i}{\Omega_e}
%         \end{equation*}
%         \item<3> \textcolor{red}{At constant blob size, increasing
%             collisionality provide a change in the filaments velocity
%             scaling properties}
%       \end{itemize}
%     \end{column}
%     \begin{column}{0.5\textwidth}
% %      \includegraphics<2>[width=\textwidth]{../pdfbox/Presentation/FigMyra}
%         \begin{tikzonimage}[width=\textwidth]{../pdfbox/Presentation/FigMyra}
%           \only<3>{
%             \draw [->, ultra thick, red] (0.7,0.3) -- (0.7,0.6);}
%         \end{tikzonimage}
%     \end{column}
%   \end{columns}
% }
% \only<4-6>{
%   \begin{columns}
%     \begin{column}{0.5\textwidth}
%       \begin{itemize}
%       \item AUG and JET \parencite{Carralero:2015gu} suggest that $\Lambda_{div}$ dominates this
%         process and a transition from
%         \textcolor{ta3chameleon}{sheath-limited}
%         \onslide<5-6>{to \textcolor{blue}{inertial regime}} 
%         \item<6> \textcolor{red}{Tested by changing n$_e$
%             and $T_e$ through fueling/seeding/heating}
%       \end{itemize}
%     \end{column}
%     \begin{column}{0.5\textwidth}
%       \begin{tikzonimage}[width=\textwidth]{../pdfbox/Presentation/KoMFig2.png}
%         \only<4-6>{
%           \draw [thick, ta3chameleon, thick] (0.45,0.25) ellipse (0.23 and 0.1);
%       }
%         \only<5-6>{
%           \draw [thick, blue, thick, rotate=-4] (0.8,0.55) ellipse (0.1 and 0.33);
%       }
%         \only<6>{
%           \draw [thick, red, thick, dashed] (0.35,0.75) circle (0.25);
%       }
%     \end{tikzonimage}
%   \end{column}
%   \end{columns}
% }
% \only<7->{
%   \begin{columns}
%     \begin{column}{0.5\textwidth}
%       \begin{itemize}
%       \item MAST \parencite{Militello:2016hk} and old TCV
%         \parencite{Garcia:2007p2615} data 
%         suggested and I$_P$ dependence. 
%           \textcolor{red}{At higher current and
%         same density SOL shoulder disappear} 
%       \item<8> \textcolor{ta3chameleon}{Being shoulder formation
%           induced by a change of $\Gamma_{\perp}$ \textit{vs}
%           $\Gamma_{\parallel}$ balance we will try to test dependence
%           on L$_{\parallel}$}
%     \end{itemize}
%     \end{column}
%     \begin{column}{0.5\textwidth}
%       \includegraphics[width=\textwidth]{../pdfbox/Presentation/FigMilitello.pdf}
%     \end{column}
%   \end{columns}
% }
% \centering{\includegraphics<1>[width=1.1\textwidth]{../pdfbox/Presentation/Fig1Presentation}}
% \end{frame}
